# WE MADE IT, INC e-commerce analysis

## Whitney Brown

### IMPORTS

```{r}
library(tidyverse)
library(tibble)
```

```{r}

shopify <- read.csv("/Users/burnesbrown1/Documents/Coding Temple/Coding_Temple_Two/capstone documents/E-commerce Dataset.csv")
```

```{r}
View(shopify)
```

```{r}
shopify_tbl <- as.tibble(shopify)

```

### VIEW TIBBLE

```{r}
view(shopify_tbl)
```

# NULL HYPOTHESIS

#1 $H0$: There is no statistically significant difference between profit from male and female patrons

$H1$ : There is a statistically significant difference between profit of male and female patrons

#2 $H0$: There is no statistically significant difference between web and mobile purchase counts

$H1$ : There is a significant difference between web and mobile purchase counts

#3 $H0$: There is no significant difference in the profitability of the electronics category compared to other categories

$H1$ : There is a significant difference in the profitability of the electronics category electronics compared to other categories

### NAME OF COLUMNS

```{r}
names(shopify_tbl)
```

### FORMAT COLUMN NAMES

```{r}
names(shopify_tbl) <- names(shopify_tbl) %>% str_to_lower()
names(shopify_tbl)
```

### LOOK FOR NULL VALUES

```{r}
colSums(is.na(shopify_tbl))
sum(is.na(shopify_tbl))

```

```{r}

#null values will be replaed with 0 due to lack of a unique identifier suggeting that the sale was either cancelled or the transaction was not completed. Replacing with a mean would artificially increase profit.

shopify_tbl_filled <- shopify_tbl %>%
  mutate(across(everything(), ~ replace_na(.,0)))
shopify_tbl_filled
```

```{r}
colSums(is.na(shopify_tbl_filled))
sum(is.na(shopify_tbl_filled))
```

-   Check column data types:

    ```{r}
    str(shopify_tbl_filled)
    ```

###Change the data types

###Change gender and device type to be Boolean:

```{r}
shopify_tbl_filled$boolean_gender <- shopify_tbl_filled$gender == "Male"
shopify_tbl_filled$boolean_device_type <-shopify_tbl_filled$device_type == "Web"
```

### Create a new column for numeric time

```{r}

time_to_seconds <- function(time_str) {
  time_sep <- as.numeric(unlist(strsplit(time_str, ":")))
  if (length(time_sep) == 3) {
    return(time_sep[1] * 3600 + time_sep[2] * 60 + time_sep[3])
  } else {
    return(NA)  
  }
}

shopify_tbl_filled$numeric_time <- sapply(shopify_tbl_filled$time, time_to_seconds)

print(shopify_tbl_filled)










```

###Create a new column to calculate %markup

```{r}
shopify_tbl_filled$percent_markup <- (shopify_tbl_filled$profit / shopify_tbl_filled$sales) * 100

```

###Change order date to numeric

```{r}
shopify_tbl_filled$order_date <- as.Date(shopify_tbl_filled$order_date)
reference_date <- as.Date("2018-01-01")  

# Calculate the numeric representation of the date
shopify_tbl_filled$numeric_order_date  <- as.numeric(shopify_tbl_filled$order_date -reference_date)

```

```{r}
shopify_tbl_filled
```

```{r}
colSums(is.na(shopify_tbl_filled))
sum(is.na(shopify_tbl_filled))
```

###Calculate %markup by product category

```{r}
grouped_shopify_tbl_filled <- shopify_tbl_filled %>%
  group_by(product_category, percent_markup)
```

```{r}
grouped_shopify_tbl_filled
```

### CORRELATION

#### Gender

```{r}

cor_gender <- cor(shopify_tbl_filled$profit, shopify_tbl_filled$boolean_gender)
print(round(cor_gender, 2))
```

### Create a dataframe with numercical columns for correlation matrix

```{r}
numerical_shopify <- subset(shopify_tbl_filled, select = -c(order_date, time, customer_id, gender,customer_login_type, product_category, device_type, product, order_priority, payment_method, percent_markup))
```

```{r}
numerical_shopify
```

```{r}
correlation_matrix <- cor(numerical_shopify)
correlation_matrix

```

```{r}
heatmap(correlation_matrix, col = colorRampPalette(c("blue", "white", "red"))(100))
View(heatmap(correlation_matrix, col = colorRampPalette(c("blue", "white", "red"))(100)))
```

### VISUALIZE DATA

```{r}
ggplot(data=numerical_shopify) +
  geom_histogram(binwidth = 1, aes(x = sales, fill = "blue"))
```

```{r}
pie = ggplot(numerical_shopify) +
  geom_bar(aes(boolean_gender, fill = TRUE),
           position = 'fill') +
  theme(aspect.ratio = 1) +
  labs(x=NULL, y=NULL)
pie + coord_polar()
```

```{r}
ggplot(data=numerical_shopify, mapping = aes(profit, boolean_gender)) + 
  geom_point()
```

```{r}
pie = ggplot(numerical_shopify) + 
  geom_bar(aes(profit, fill = boolean_gender),
           position = 'fill') +
  theme(aspect.ratio=1)+
  labs(x=NULL, y=NULL)

pie + coord_polar()
```



```{r}

t.test(numerical_shopify$boolean_gender, numerical_shopify$sales)

```

```{r}
t.test(numerical_shopify$boolean_gender, numerical_shopify$profit)

```

```{r}
t.test(numerical_shopify$sales, numerical_shopify$boolean_device_type)


```
```{r}
fit <- lm(boolean_gender~ profit, data=numerical_shopify)
fit <- lm(numerical_shopify$boolean_gender, numerical_shopify$profit)
fit

```


```{r}
summary(fit)
```

```{r}

fit <- lm(boolean_gender~ sales, data=numerical_shopify)
fit <- lm(numerical_shopify$boolean_gender, numerical_shopify$sales)
fit
 
```

```{r}
summary(fit)
```
### RESULTS IN REPORT
